Changes to police demand in COVID-19 pandemic

### 2022-03-14 docs/index.Rmd
why aren't the charts working arghh
updating n8 presentation

Explore changes over the pandemic and associated lockdowns in calls to service and response

@@

library(lubridate)
library(tidyverse)
library(tsibble)
library(sf)

all_calls <- read_rds("/Volumes/n8_covid/all_calls_forecast.Rds")
call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
attended_by_grade_forecast <- read_rds("/Volumes/n8_covid/attended_by_grade_forecasts.Rds")
domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")
domestic_by_grade_attended_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_attended_forecasts.Rds")
by_grade_tos_forecasts <- read_rds("/Volumes/n8_covid/by_grade_tos_forecasts.Rds")
cheshire_lsoas <- st_read("cheshire_lsoas.geojson")
lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "Pre-COVID"), 
                         data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "2020"))
total_calls_by_imd <- read_csv("/Volumes/n8_covid/total_calls_by_imd.csv")
weekly_count_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_count_by_lsoa.csv")
weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")

@@

@@

@@

# Call types: Domestic incidents

@@

# Call types: Domestic incidents
This does not change when we break down by grade of call.

@@

# Police response: Attendance rate

@@

# Police response: Attendance rate

@@

# Police response: Response time

@@

# Police response: Time on scene

Need alltogether time on scene graph here

# Police response: Time on scene

@@

@@

# Origin of calls: IMD

@@

# Origin of calls: IMD

@@

# Origin of calls: IMD for ASB calls

@@

>>>>

Explore changes in calls for service and response over the pandemic and associated lockdowns.

@@

library(lubridate)
library(tidyverse)
library(tsibble)
library(sf)
library(ineq)

all_calls <- read_rds("/Volumes/n8_covid/all_calls_forecast.Rds")
call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
attended_by_grade_forecast <- read_rds("/Volumes/n8_covid/attended_by_grade_forecasts.Rds")
domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")
domestic_by_grade_attended_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_attended_forecasts.Rds")
by_grade_tos_forecasts <- read_rds("/Volumes/n8_covid/by_grade_tos_forecasts.Rds")
cheshire_lsoas <- st_read("../cheshire_lsoas.geojson")
lsoa_filler <- bind_rows(data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "Pre-COVID"), 
                         data.frame(lsoa = unique(cheshire_lsoas$LSOA11NM),
                          pre_post = "2020"))
total_calls_by_imd <- read_csv("/Volumes/n8_covid/total_calls_by_imd.csv")
weekly_count_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_count_by_lsoa.csv")
weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")
# gini_asb <- read_rds("/Volumes/n8_covid/gini_asb_forecast.Rds")

@@

---
class: center, middle, inverse

@@

---
class: center, middle, inverse

# Changes in call types

@@

# Domestic incidents

@@

# Domestic incidents
This does not change when we break down by grade of call.

@@

---
class: center, middle, inverse
# Police response

---
class: center, middle
# Attendance rate

@@

---
class: center, middle
# Attendance rate

@@

---
class: center, middle
# Response time

@@

---
class: center, middle
# Time on scene

@@

---
class: center, middle, inverse
# Change in nature of the demand

@@

# Index of Multiple Deprivation

@@

# No change for overall calls

@@

# Increase of calls recorded as ASB (concern over COVID-19 breach) from less deprived areas

@@

# Less concentration of calls

```{r giniASB, fig.width=11,fig.height=7}

make_gini_plot <- function(x){

  weekly_gini <- x %>% 
    group_by(inc_wk) %>% 
    summarise(gini = ineq(n), type = "Gini")

  ggplot(weekly_gini, aes(x = inc_wk, y = gini)) + 
    geom_line() + 
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0.35, label = row), data = dates, colour = "grey20") +
    scale_x_date(date_labels = "%e %b\n%Y", 
                 limits = as.Date(c("2015-01-01", "2020-12-21")))+
    labs(
      title = "Gini coefficient* over time",
      subtitle = "*measure of inequality with 0 = perfect equality and 1 = maximal inequality",
      x = NULL,
      y = "Gini coefficient") +
    theme_minimal() +
    theme(plot.title = element_text(face = "bold"))
}

make_gini_plot(weekly_asb_by_lsoa)

# Overall
